\documentclass[a4paper, 12pt]{article}

% Package for page dimensions
\usepackage[scale=0.9, top=.5in, bottom=.5in]{geometry}

% Package for no indentation and adjusting paragraph spacing
\usepackage{parskip} 

% Packages for fonts and icons
\usepackage{fontspec}
\usepackage{fontawesome5}


% Packages for tables
\usepackage{tabularx}
\newcolumntype{C}{>{\centering\arraybackslash}X}

% Packages for section titles
\usepackage{titlesec}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{6pt}

% Package for colors
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{linkblue}{RGB}{60, 120, 216}
\definecolor{regtextgray}{RGB}{102, 102, 102}
\definecolor{imptextblack}{RGB}{0, 0, 0}

% Package for hyperlinks
\usepackage[unicode, hidelinks]{hyperref}
\hypersetup{colorlinks=true, allcolors=linkblue}

% Packages for lists within sections
\usepackage{enumitem}

% Package for bibliography
% \usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
% \addbibresource{citations.bib}

% Set main font
\setmainfont{Arial}

\begin{document}
\color{regtextgray} % regular text color
\pagestyle{empty} % non-numbered pages

% Title Section
\begin{tabularx}{\linewidth}{@{} C @{}}
    \textcolor{imptextblack}{\Huge{\textbf{IMRAN YAFITH}}}                                    \\[6pt]
    \underline{\href{mailto:imranpyafith@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} imranpyafith@gmail.com}} $|$
    \underline{\href{https://imranyafith.com/}{\raisebox{-0.05\height}{\faGlobe} imranyafith.com}} $|$
    \underline{\href{tel:+16476873213}{\raisebox{-0.05\height}{\faMobile} +1 (647) 687-3213}} \\
    \underline{\href{https://github.com/pixelfox01}{\raisebox{-0.05\height}{\faGithub} github.com/pixelfox01/}} $|$
    \underline{\href{https://www.linkedin.com/in/imran-yafith-95a437266/}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/imran-yafith}}
\end{tabularx}

% Summary Section
% \begin{center}
%     \fontsize{11pt}{12pt}\selectfont
%     Dedicated third-year Computer Science student with a strong foundation in data structures and algorithms and a keen interest in problem-solving and optimizing code efficiency.
%     Experience in building, testing and deploying user-focused applications using modern technologies and frameworks.
% \end{center}

\vspace{6pt}

% Education Section
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l X@{} }
    \textcolor{imptextblack}{\textbf{Honours Bachelor of Computer Science}} & \hfill Sep. 2021 --- Apr. 2026 \\
    \small{Sheridan College $|$ GPA:\ 3.82}
\end{tabularx}
\begin{center}
    \begin{tabular}{@{} r @{\hspace{2em}} p{0.7\textwidth} @{}}
        \textcolor{imptextblack}{\textbf{Relevant Coursework}} & Data Structures \& Algorithms, C/C++ Program Design, Enterprise Software Systems, Distributed \& Parallel Computing, Cloud Infrastructure                                                                                                             \\
        \textcolor{imptextblack}{\textbf{Extra-curricular}}    & \href{https://devpost.com/software/cybernexus}{\textit{Hackville '23 Winner}}, \href{https://devpost.com/software/pitchperfect-teu3zs}{\textit{Hackville '24 Participant}}, Executive of the Sheridan Computer Science Club, Python Programming Tutor \\
    \end{tabular}
\end{center}

% Professional Experience Section
\section{Professional Experience}

\textcolor{imptextblack}{\textbf{Naryant (Sheridan CAAI) --- Research Assistant}} \hfill Oct. 2023 --- Present
\begin{itemize}[nosep, after=\strut, itemsep=2pt]
    % \small
    \item Utilized \textcolor{imptextblack}{\textit{Simulation of Urban Mobility (SUMO)}}
          and \textcolor{imptextblack}{\textit{OpenStreetMap (OSM)}} to model and analyze
          traffic patterns across \textcolor{imptextblack}{\textbf{10+}} urban zones,
          enhancing data accuracy for urban development projects.
    \item Synthesized a comprehensive dataset predicting traffic demand for the city of
          \textcolor{imptextblack}{\textit{Oakville}}, utilizing simulation tools (SUMO,
          OSM).
    \item Collaborated with a team of \textcolor{imptextblack}{\textbf{4 researchers}} to
          assimilate simulation data, bolstering collective strategic planning and
          decision-making.
\end{itemize}

\textcolor{imptextblack}{\textbf{Karmy Pain Clinic (Sheridan CAAI) --- Research Assistant}} \hfill Dec. 2022 --- Aug. 2023
\begin{itemize}[nosep, after=\strut, itemsep=2pt]
    % \small
    \item Engineered an AI-driven pain diagnostic system leveraging
          \textcolor{imptextblack}{\textit{Python}} and
          \textcolor{imptextblack}{\textit{MATLAB}}, improving patient diagnosis accuracy
          and treatment efficacy, reducing diagnosis time.
    \item Increased data processing accuracy by \textcolor{imptextblack}{\textbf{30\%}}
          with improved data analysis techniques.
    \item Contributed to a \textcolor{imptextblack}{\textbf{5 person}} team's iterative
          development and optimization of an AI model, achieving significant accuracy
          gains based on patient feedback and trials.
\end{itemize}

% Skills Section
\section{Skills}
\begin{center}
    \begin{tabular}{@{\hspace{1em}} r @{\hspace{2em}} p{0.65\textwidth} @{}}
        \textcolor{imptextblack}{\textbf{Programming Languages}} & Python, JavaScript, TypeScript, C\#, C++, C           \\
        \textcolor{imptextblack}{\textbf{Frameworks \& Tools}}   & React, NextJS, Node.js, Express, .NET, Xamarin, Flask \\
        \textcolor{imptextblack}{\textbf{Datastores}}            & MongoDB, Firebase (Firestore), SQL Server, SQLite     \\
        \textcolor{imptextblack}{\textbf{DevOps}}                & AWS, Git, GitHub, Docker                              \\
    \end{tabular}
\end{center}

% Projects Section
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
    \href{https://imranyafith.com/}{\underline{\textbf{imranyafith.com \faIcon{external-link-alt}}}} & \hfill \href{https://github.com/pixelfox01/imranyafith.com}{\small github.com/pixelfox01/imranyafith.com} \\
    \small{Next.js, TypeScript, React, TailwindCSS}
\end{tabularx}
\vspace{-12pt}
\begin{itemize}[nosep, after=\strut, itemsep=2pt]
    \item Personal portfolio website made to showcase professional skills and projects.
    \item Utilized \textcolor{imptextblack}{\textit{Next.js}} for server-side rendering
          and \textcolor{imptextblack}{\textit{TailwindCSS}} for styling.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
    \href{https://mern-bookstore-demo.vercel.app/}{\underline{\textbf{Bookstore App  \faIcon{external-link-alt}}}} & \hfill \href{https://github.com/pixelfox01/mern-bookstore-demo}{\small github.com/pixelfox01/mern-bookstore-demo} \\
    \small{MongoDB, Express, React (Vite), Node.js, TypeScript}
\end{tabularx}
\vspace{-12pt}
\begin{itemize}[nosep, after=\strut, itemsep=2pt]
    \item Full-stack bookstore application, featuring
          \textcolor{imptextblack}{\textit{complete CRUD operations}} and
          \textcolor{imptextblack}{\textit{MongoDB}} integration.
    \item Utilized \textcolor{imptextblack}{\textit{React (Vite)}} for faster frontend
          development and \textcolor{imptextblack}{\textit{TailwindCSS}} for styling.
    \item Implemented backend API with \textcolor{imptextblack}{\textit{Express}} and
          \textcolor{imptextblack}{\textit{Node.js}}.
\end{itemize}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
    \textcolor{imptextblack}{\underline{\textbf{Homebase Automation}}} & \hfill \href{https://github.com/pixelfox01/HomebaseAutomation}{\small github.com/pixelfox01/homebase-automation} \\
    \small{Python, BeautifulSoup4, Playwright, Google Developer API}                                                                                                                      \\
\end{tabularx}
\vspace{-12pt}
\begin{itemize}[nosep, after=\strut, itemsep=2pt]
    \item Shift reminder application intergrated with
          \textcolor{imptextblack}{\textit{Google Calendar}} for real-time notifications.
\end{itemize}
\end{document}
